%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/QiuHaohao}{\Large Qiu Haoze}} & Email : \href{mailto:qiuh0008@e.ntu.edu.sg}{qiuh0008@e.ntu.edu.sg}\\
  \href{}{} & Mobile : +65-8345-4608 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nanyang Technological University}{Singapore}
      {Bachelor of Engineering in Computer Science;  GPA: \textbf{4.88}/5.00}{Aug. 2016 -- Present}
  \resumeSubHeadingListEnd




%-----------INTERNSHIP EXPERIENCE-----------------
\section{Internship Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Labs, Garena Online Private Limited}{Singapore}
      {Software Engineer Intern}{Aug 2018 - Present}
      \resumeItemListStart
        \resumeItem{SeaTalk Web}
          {SeaTalk is a Instant Messaging APP for business. Involved in Web front-end development of SeaTalk Web in JavaScript using React and Redux.}
      \resumeItemListEnd

    \resumeSubheading
      {Juniper Networks}{Singapore}
      {System Engineer Intern}{May 2018 - Aug 2018}
      \resumeItemListStart
        \resumeItem{BOMBot}
          {A Slack chatbot that proposes BOM(Bill of Material) and recommends Juniper SRX Firewall products to customers. Involved in the design and development the chatbot in Python, using Amazon Lex, AWS lambda and various other AWS services. Automated the infrastructure provision with AWS CloudFormation.}
      \resumeItemListEnd

    \resumeSubheading
      {Shopee}{Singapore}
      {Data Scientist Intern}{Dec 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{SKU Clustering}
          {Worded on the NLP problem  to cluster item listing on the e-commerce platform into SKUs, using scikit-learn, gensim and nltk in Python. Proposed a new approach to the problem and improved the performance measure by 10\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Nanyang Technological University}{Singapore}
      {Research Assistant}{May 2018 - Aug 2018}
      \resumeItemListStart
        \resumeItem{Study on Affective States of E-lectures Learners}
          {Research on machine learning for predicting e-lecture learner's affective states using Two-Stream Networks built with PyTorch. Conducted experiments for data collection.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%-----------ACADEMIC PROJECTS-----------------
\section{Academic Project}
  \resumeSubHeadingListStart
    \resumeSubheading
      {URECA Undergraduate Research Program}{Singapore}
      {Privacy issues and protection measures of Blockchain Protocol}{Aug 2017 - July 2018}
    \resumeItemListStart
        \item
          {Research on privacy-ensuring Blockchain with Homomorphic Encryption. Involved in development of a proof-of-concept Blockchain application using GoLang.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%--------AWARDS & ACHIEVEMENTS------------
\section{Awards \& Achievements}
 \resumeSubHeadingListStart
   \item{
     AY 2016/2017, AY 2017/2018 \textbf{Dean's List}, College of Engineering, Nanyang Technological University
   }
   \item{
     PRC SM2 Scholarship(NTU Sci \& Tech Scholarship), 2015
   }
   \item{
     China National Biology Olympiad(Fujian) \textbf{Gold Medalist}, 2015
   }
 \resumeSubHeadingListEnd

% --------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Fluent in \textbf{English}, \textbf{Mandarin} and \textbf{Japanese}}
   }
   \item{
     \textbf{Programming Languages:}%{: Python, Java, JavaScript, Scheme/Lisp}
     \resumeItemListStart
        \item
          \textbf{Python}{: My first language. Used in an Open Source project. Written a few tools for personal use.}
        \item
          \textbf{Java}{: Written an implementation of Blockchain and a school project}
        \item
          \textbf{JavaScript}{: Web front-end development with React and Redux in previous internship experience}
        \item
          \textbf{Scheme/Lisp}{: Worked through the book `Structure and Interpretation of Computer Programs'}
      \resumeItemListEnd
   }
 \resumeSubHeadingListEnd

%-----------LEADERSHIP / CO-CURRICULAR ACTIVITIES-----------------
\section{Leadership / Co-curricular Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Guitar Ensemble, Nanyang Technological University}{Singapore}
      {Chairperson/Vice Chairperson}{May 2018 - Present/Aug 2017 - May 2018}
      \resumeItemListStart
        \item{Running a club with around 50 members.}
        \item{Organised a trip to Japan with 15 members participating.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------VOLUNTEER EXPERIENCE-----------------
\section{Volunteer Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SCSE Peer Tutoring Program}{}
      {Peer Tutor}{Feb 2017 - April 2017}
      \resumeItemListStart
        \item{Conducted tutorial of the course “CZ1006 - Computer Architecture” for peer students}
      \resumeItemListEnd
    \resumeSubheading
      {Code in the Community}{}
      {Instructor}{Jan 2017 - April 2017}
      \resumeItemListStart
        \item{Conducted python class for around 12 children at Canberra CC.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
.

%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%   \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

